Blocking-resistant communication through high-value web services

### 2014-05-12 docs/meek.tex
"Background and related work"
Bare cite for CloundTransport (PETS 2014).
Better abstract.

\begin{abstract}
We describe meek, a blocking-resistant Internet communication system for censorship circumvention.
A key technique we use is ``domain fronting''---communicating with
a forbidden domain name while appearing to communicate with one that is allowed.
\end{abstract}

@@

\section{Related work}

@@

>>>>

\begin{abstract}
We describe meek, a blocking-resistant Internet communication system for censorship circumvention.
meek uses HTTP as a mechanism for transporting data, but it is not a steganographic HTTP transport;
rather, it relies on HTTPS to hide the contents of communications from a censor.
Communications are proxied through a web service that may itself be blocked by the censor:
``domain fronting''---in which the domain name used in the (censor-visible)
DNS request and TLS server name extension doesn't match the name in the (censor-invisible)
HTTP host header---enables communication that is apparently with an allowed host
but actually with a forbidden host.

Though HTTPS frustrates blocking by hiding the underlying communication,
differences in TLS implementations give rise to distinguishing features
that may be used to block circumvention traffic.
We describe how we use a web browser as a tool for making HTTPS requests,
so that the TLS signature of circumvention traffic resembles that of ordinary web browsing.
We present other, more subtle traffic characteristics that may enable blocking,
and identify potential countermeasures to such blocking.

We describe our experience implementing meek as a pluggable transport for Tor,
and the results of an initial experimental deployment.
\end{abstract}

@@

\section{Background and related work}

@@

CloudTransport~\cite{cloudtransport}
